\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-08-24 smurf_paper.tex
affiliations should really be the ones that paid for SCUBA-2 work

\author[Edward~L.~Chapin~et~al.]{
  \parbox[t]{\textwidth}{
    Edward~L.~Chapin$^{1,2,3}$\thanks{E-mail:~echapin@sciops.esa.int},
    David~S.~Berry$^{3}$,
    Andrew~G.~Gibb$^{2}$,
    Tim~Jenness$^{3}$,
    Douglas~Scott$^{2}$,
    Frossie~Economou$^3$\thanks{Present address: National Optical
      Astronomy Observatory, 950 N.\ Cherry Avenue, Tucson, AZ 85719, USA}
  }
  \\
  \\
  $^{1}$XMM SOC, ESAC, Apartado 78, 28691 Villanueva de la Ca\~nada, Madrid,
  Spain\\
  $^{2}$Dept. of Physics \& Astronomy, University of British Columbia,
  6224 Agricultural Road, Vancouver, B.C. V6T 1Z1, Canada\\
  $^{3}$JointAstronomy Centre, 660 N. A`oh\={o}k\={u} Place, University
  Park, Hilo, Hawaii 96720, USA}

>>>>

\author[Edward~L.~Chapin~et~al.]{
  \parbox[t]{\textwidth}{
    Edward~L.~Chapin$^{1,2}$\thanks{E-mail:~echapin@sciops.esa.int,
      Present address: XMM SOC, ESAC, Apartado 78, 28691 Villanueva de
      la Ca\~nada, Madrid, Spain},
    David~S.~Berry$^{2}$,
    Andrew~G.~Gibb$^{1}$,
    Tim~Jenness$^{2}$,
    Douglas~Scott$^{1}$,
    Frossie~Economou$^2$\thanks{Present address: National Optical
      Astronomy Observatory, 950 N.\ Cherry Avenue, Tucson, AZ 85719, USA}
  }
  \\
  \\
  $^{1}$Dept. of Physics \& Astronomy, University of British Columbia,
  6224 Agricultural Road, Vancouver, B.C. V6T 1Z1, Canada\\
  $^{2}$JointAstronomy Centre, 660 N. A`oh\={o}k\={u} Place, University
  Park, Hilo, Hawaii 96720, USA}
